---
title: "Untitled"
author: "Jacqueline Park"
date: "2025-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
rm(list=ls())
library(readr)
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(countrycode)
library(WDI)
library(fixest)
library(marginaleffects)
library(desta)
# library(plotly) # for 3D plots

```



# Load the data
```{r}
df = read.csv("NTE_IPR_final_v2.csv")
```


# Descriptive works
## China's score trend
```{r}
chinadf = df %>% filter(country == "CHINA")
plot(chinadf$year, chinadf$deberta_score, type = "b", pch = 16)
```


## Japan's score trend
```{r}
japdf = df %>% filter(country == "JAPAN")
plot(japdf$year, japdf$deberta_score, type = "b", pch = 16)
```


## EU's score trend
```{r}
eudf = df %>% filter(country == "EUROPEAN UNION")
plot(eudf$year, eudf$deberta_score, type = "b", pch = 16)
```


## Mexico's score trend
```{r}
mexdf = df %>% filter(country == "MEXICO")
plot(mexdf$year, mexdf$deberta_score, type = "b", pch = 16)
```


## Canada's score trend
```{r}
candf = df %>% filter(country == "CANADA")
plot(candf$year, candf$deberta_score, type = "b", pch = 16)
```



## Key countries' trend in glance
```{r}
ctyplotdt = df %>%
  distinct(country, year, .keep_all = T) %>%
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(cumcount = n()) %>%
  filter(
           country == "RUSSIA" |
           country == "CHINA" | country == "EUROPEAN UNION" | 
           country == "BRAZIL" | country == "JAPAN" |
           country == "INDIA" | country == "MEXICO" )

ggplot(data = ctyplotdt,
       aes(x = year, y = deberta_score, color = country)) + geom_smooth(se=F) +
  labs(x = "Year", y = "DeBERTa score", color = "Country") + scale_color_manual(
    values = c("red", "orange", "green", "steelblue", "cyan", "yellow", "magenta")
  ) + theme_minimal()

```



# Data prep for analysis
## Basics (PTA, BIT, OECD)
```{r}
## subset data
bertdf = df %>% select(-text)

## US PTA
bertdf$uspta = ifelse(bertdf$country=="AUSTRALIA" & bertdf$year>=2004|
                     bertdf$country=="BAHRAIN" & bertdf$year>=2004|
                     bertdf$country=="COSTA RICA" & bertdf$year>=2004|
                     bertdf$country=="EL SALVADOR" & bertdf$year>=2004|
                     bertdf$country=="GUATEMALA" & bertdf$year>=2004|
                     bertdf$country=="HONDURAS" & bertdf$year>=2004|
                     bertdf$country=="NICARAGUA" & bertdf$year>=2004|
                     bertdf$country=="DOMINICAN REPUBLIC" & bertdf$year>=2004|
                     bertdf$country=="CHILE" & bertdf$year>=2003|
                     bertdf$country=="COLOMBIA" & bertdf$year>=2006|
                     bertdf$country=="ISRAEL" & bertdf$year>=1985|
                     bertdf$country=="JORDAN" & bertdf$year>=2000|
                     bertdf$country=="KOREA" & bertdf$year>=2007|
                     bertdf$country=="MOROCCO" & bertdf$year>=2004|
                     bertdf$country=="CANADA" & bertdf$year>=1992|
                     bertdf$country=="MEXICO" & bertdf$year>=1992|
                     bertdf$country=="OMAN" & bertdf$year>=2006|
                     bertdf$country=="PANAMA" & bertdf$year>=2007|
                     bertdf$country=="PERU" & bertdf$year>=2006|
                     bertdf$country=="SINGAPORE" & bertdf$year>=2003|
                     bertdf$country=="CHINA" & bertdf$year>=2020|
                     bertdf$country=="VIETNAM" & bertdf$year>=2000, 1, 0)

## US BITs
bertdf$usbit = ifelse(bertdf$country=="ALBANIA" & bertdf$year>=1995|
                     bertdf$country=="ALGERIA" & bertdf$year>=2001|
                     bertdf$country=="ARGENTINA" & bertdf$year>=1991|
                     bertdf$country=="ARMENIA" & bertdf$year>=1992|
                     bertdf$country=="AZERBAIJAN" & bertdf$year>=1997|
                     bertdf$country=="BAHRAIN" & bertdf$year>=1999|
                     bertdf$country=="BANGLADESH" & bertdf$year>=1986|
                     bertdf$country=="BELARUS" & bertdf$year>=1994|
                     bertdf$country=="BOLIVIA" & bertdf$year>=1998|
                     bertdf$country=="BULGARIA" & bertdf$year>=1993|
                     bertdf$country=="CAMEROON" & bertdf$year>=1986|
                     bertdf$country=="COSTA RICA" & bertdf$year>=1995|
                     bertdf$country=="CONGO" & bertdf$year>=1994|
                     bertdf$country=="DOMINICAN REPUBLIC" & bertdf$year>=2005|
                     bertdf$country=="ECUADOR" & bertdf$year>=1993|
                     bertdf$country=="EGYPT" & bertdf$year>=1986|
                     bertdf$country=="GEORGIA" & bertdf$year>=1994|
                     bertdf$country=="GHANA" & bertdf$year>=1998|
                     bertdf$country=="GUATEMALA" & bertdf$year>=1986|
                     bertdf$country=="HAITI" & bertdf$year>=1983|
                     bertdf$country=="HONDURAS" & bertdf$year>=2001|
                     bertdf$country=="JAMAICA" & bertdf$year>=1994|
                     bertdf$country=="JORDAN" & bertdf$year>=1997|
                     bertdf$country=="KAZAKHSTAN" & bertdf$year>=1994|
                     bertdf$country=="KENYA" & bertdf$year>=2000|
                     bertdf$country=="KYRGYZSTAN" & bertdf$year>=1993|
                     bertdf$country=="NICARAGUA" & bertdf$year>=1995|
                     bertdf$country=="PANAMA" & bertdf$year>=1982|
                     bertdf$country=="PARAGUAY" & bertdf$year>=1991|
                     bertdf$country=="PHILIPPINES" & bertdf$year>=1989|
                     bertdf$country=="POLAND" & bertdf$year>=1990|
                     bertdf$country=="ROMANIA" & bertdf$year>=1994|
                     bertdf$country=="SRI LANKA" & bertdf$year>=1991|
                     bertdf$country=="TUNISIA" & bertdf$year>=1990|
                     bertdf$country=="TURKEY" & bertdf$year>=1985|
                     bertdf$country=="UKRAINE" & bertdf$year>=1994|
                     bertdf$country=="UZBEKISTAN" & bertdf$year>=1994, 1, 0)

## OECD bf 1994 status
bertdf$oecd1994 = ifelse(bertdf$country=="AUSTRIA"|bertdf$country=="BELGIUM"|
                        bertdf$country=="CANADA"|bertdf$country=="DENMARK"|
                        bertdf$country=="FRANCE"|bertdf$country=="GERMANY"|
                        bertdf$country=="GREECE"|bertdf$country=="ICELAND"|
                        bertdf$country=="IRELAND"|bertdf$country=="ITALY"|
                        bertdf$country=="LUXEMBOURG"|
                          bertdf$country=="NETHERLANDS"|
                        bertdf$country=="NORWAY"|bertdf$country=="PORTUGAL"|
                        bertdf$country=="SPAIN"|bertdf$country=="SWEDEN"|
                        bertdf$country=="SWITZERLAND"|bertdf$country=="TURKEY"|
                        bertdf$country=="UNITED KINGDOM"|bertdf$country=="JAPAN"|
                        bertdf$country=="FINLAND"|bertdf$country=="AUSTRALIA", 1, 0)

## OECD status
bertdf$oecd = ifelse(bertdf$country=="CHILE" & bertdf$year>=2010|
                    bertdf$country=="COLOMBIA" & bertdf$year>=2020|
                    bertdf$country=="COSTA RICA" & bertdf$year>=2021|
                    bertdf$country=="CZECH REPUBLIC" & bertdf$year>=1995|
                    bertdf$country=="HUNGARY" & bertdf$year>=1996|
                    bertdf$country=="ISRAEL" & bertdf$year>=2010|
                    bertdf$country=="KOREA" & bertdf$year>=1996|
                      bertdf$country=="MEXICO" & bertdf$year>=1994|
                    bertdf$country=="POLAND" & bertdf$year>=1996|
                    bertdf$oecd1994==1, 1, 0)

## assign iso codes
bertdf = bertdf %>% dplyr::mutate(
  country = str_to_title(country),
  iso3c = countrycode(country, 
                      origin = "country.name",
                      destination = "iso3c",
                      custom_match = c("European Union" = "EUU"))
)

```


## Special 301 status
```{r}
## Special 301
special301=read.csv("special301.csv")
colnames(special301) = gsub("X", "", colnames(special301))
special301 = as.data.frame(gsub("[[:punct:]]", "", as.matrix(special301))) 
special301 = as.data.frame(gsub("Monitoring|Pending", "", as.matrix(special301)))

special301 = special301 %>%
  pivot_longer(cols = c(2:15),
               names_to = "year",
               values_to = "special301")

special301$Country = replace(special301$Country, special301$Country == "South Korea", "Korea")
names(special301)[names(special301)=="Country"]="country"
special301$year=as.numeric(special301$year)

bertdf = bertdf %>%
  left_join(special301, join_by(country, year))

bertdf$country = str_to_upper(bertdf$country)

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==1995&(bertdf$country=="BRAZIL"|
                                                     bertdf$country=="EUROPEAN UNION"|
                                                     bertdf$country=="GREECE"|
                                                     bertdf$country=="INDIA"|
                                                     bertdf$country=="JAPAN"|
                                                     bertdf$country=="KOREA"|
                                                     bertdf$country=="SAUDI ARABIA"|
                                                     bertdf$country=="TURKEY"), "PWL")
bertdf$special301=replace(bertdf$special301,
                             bertdf$year==1995&(bertdf$country=="ARGENTINA"|
                                                     bertdf$country=="BAHRAIN"|
                                                     bertdf$country=="CANADA"|
                                                     bertdf$country=="CHILE"|
                                                     bertdf$country=="CHINA"|
                                                     bertdf$country=="COLOMBIA"|
                                                     bertdf$country=="COSTA RICA"|
                                                     bertdf$country=="EGYPT"|
                                                     bertdf$country=="EL SALVADOR"|
                                                     bertdf$country=="GUATEMALA"|
                                                     bertdf$country=="INDONESIA"|
                                                     bertdf$country=="ITALY"|
                                                     bertdf$country=="PAKISTAN"|
                                                     bertdf$country=="PERU"|
                                                     bertdf$country=="PHILIPPINES"|
                                                     bertdf$country=="POLAND"|
                                                     bertdf$country=="ROMANIA"|
                                                     bertdf$country=="RUSSIA"|
                                                     bertdf$country=="SINGAPORE"|
                                                     bertdf$country=="SOUTH AFRICA"|
                                                     bertdf$country=="THAILAND"|
                                                     bertdf$country=="TAIWAN"|
                                                     bertdf$country=="UNITED ARAB EMIRATES"|
                                                     bertdf$country=="VENEZUELA"), "WL")

bertdf$special301 = replace(bertdf$special301, 
                               bertdf$year==1996 & grepl("china", bertdf$country, ignore.case = T),
                               "PFC")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1996 & grepl("argentina|european|greece|
                                                            india|indonesia|japan|
                                                            korea|turkey",
                                                            bertdf$country, ignore.case = T),
                               "PWL")
bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1996 & grepl("australia|bahrain|brazil|
                                                            canada|chile|colombia|costa|
                                                            ecuador|egypt|salvador|guatemala|
                                                            italy|kuwait|oman|pakistan|paraguay|
                                                            peru|philipp|poland|russia|saudi|
                                                            singapore|thailand|emirates|venezuela",
                                                            bertdf$country, ignore.case = T),
                               "WL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1997 & grepl("argentina|ecuador|egypt|
                                                            european|greece|india|
                                                            indonesia|paraguay|russia|
                                                            turkey",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1997 & grepl("australia|bahrain|bolivia|
                                                            brazil|bulgaria|canada|
                                                            chile|colombia|costa|denmark|
                                                            dominican|guatemala|honduras|
                                                            hong kong|ireland|israel|italy|
                                                            japan|jordan|korea|kuwait|
                                                            luxembourg|oman|pakistan|panama|
                                                            peru|philipp|poland|saudi|
                                                            singapore|sweden|thailand|
                                                            emirates|venezuela",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1998 & grepl("paraguay",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PFC")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1998 & grepl("argentina|bulgaria|dominican|
                                                            ecuador|egypt|european|
                                                            greece|india|
                                                            indonesia|israel|italy|
                                                            kuwait|macao|russia|
                                                            turkey",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1998 & grepl("australia|bahrain|canada|
                                                            chile|colombia|costa|czech|
                                                            denmark|guatemala|honduras|
                                                            hong kong|ireland|jamaica|
                                                            japan|jordan|kazakh|korea|
                                                            oman|pakistan|peru|philipp|
                                                            poland|qatar|saudi|
                                                            singapore|africa|sweden|thailand|
                                                            ukraine|emirates|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1999 & grepl("argentina|dominican|
                                                            egypt|european|
                                                            greece|guatema|india|
                                                            indonesia|israel|italy|
                                                            kuwait|macao|macau|
                                                            peru|russia|turkey|ukraine",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==1999 & grepl("australia|belarus|bolivia|brazil|canada|
                                                            chile|colombia|costa|czech|
                                                            denmark|ecuador|hungary|
                                                            ireland|jamaica|
                                                            japan|jordan|korea|lebanon|
                                                            mexico|zealand|
                                                            oman|pakistan|philipp|
                                                            poland|qatar|romania|saudi|
                                                            singapore|africa|spain|sweden|
                                                            taiwan|thailand|
                                                            ukraine|emirates|uruguay|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2000 & grepl("argentina|dominican|
                                                            egypt|european|
                                                            greece|guatema|india|
                                                            israel|italy|korea|
                                                            malaysia|peru|
                                                            poland|russia|turkey|ukraine",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2000 & grepl("armenia|azerbaijan|belarus|bolivia|brazil|canada|
                                                            chile|colombia|costa|czech|
                                                            denmark|ecuador|hungary|indonesia|
                                                            ireland|jamaica|kazakh|
                                                            kuwait|latvia|lebanon|
                                                            lithuania|macao|macau|
                                                            moldova|oman|pakistan|philipp|
                                                            poland|qatar|romania|saudi|
                                                            singapore|spain|taiwan|tajiki|thailand|
                                                            turkmen|uruguay|uzbek|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2001 & grepl("argentina|costa|dominican|
                                                            egypt|european|hungary|india|
                                                            indonesia|israel|korea|
                                                            lebanon|malaysia|philipp|
                                                            russia|taiwan|uruguay",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2001 & grepl("armenia|azerbaijan|belarus|bolivia|brazil|canada|
                                                            chile|colombia|greece|
                                                            guatemala|italy|jamaica|kazakh|
                                                            kuwait|latvia|lithuania|
                                                            lithuania|macao|macau|
                                                            zealand|pakistan|peru|
                                                            poland|romania|saudi|slovak|
                                                            tajiki|thailand|turkey|
                                                            turkmen|emirates|uzbek|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2002 & grepl("ukraine",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PFC")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2002 & grepl("argentina|brazil|colombia|dominican|
                                                            egypt|european|hungary|india|
                                                            indonesia|israel|
                                                            lebanon|philipp|
                                                            russia|taiwan|uruguay",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")

bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2002 & grepl("armenia|azerbaijan|bahamas|belarus|
                                                            bolivia|canada|costa|greece|
                                                            guatemala|italy|jamaica|kazakh|korea|
                                                            kuwait|latvia|lithuania|
                                                            lithuania|zealand|pakistan|peru|
                                                            poland|qatar|romania|saudi|slovak|
                                                            tajiki|thailand|turkey|
                                                            turkmen|uzbek|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2003 & grepl("ukraine",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PFC")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2003 & grepl("argentina|bahamas|brazil|european|
                                                            india|indonesia|lebanon|philipp|
                                                            poland|russia|taiwan",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2003 & grepl("azerbaijan|belarus|
                                                            bolivia|canada|chile|
                                                            colombia|costa|croatia|
                                                            dominican|ecuador|egypt|
                                                            guatemala|hungary|israel|
                                                            italy|jamaica|kazakh|korea|
                                                            kuwait|latvia|lithuania|
                                                            malaysia|mexico|
                                                            pakistan|peru|romania|saudi|slovak|
                                                            tajiki|thailand|turkey|
                                                            uzbek|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")



bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2004 & grepl("ukraine",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PFC")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2004 & grepl("argentina|bahamas|brazil|egypt|european|
                                                            india|indonesia|korea|
                                                            kuwait|lebanon|philipp|
                                                            russia|taiwan|turkey",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "PWL")


bertdf$special301 = replace(bertdf$special301,
                               bertdf$year==2004 & grepl("azerbaijan|belarus|belize|
                                                            bolivia|bulgaria|canada|chile|
                                                            colombia|costa|croatia|
                                                            dominican|ecuador|
                                                            guatemala|hungary|israel|
                                                            italy|jamaica|kazakh|
                                                            latvia|lithuania|malaysia|mexico|
                                                            peru|poland|romania|saudi|slovak|
                                                            tajiki|thailand|turkmen|uruguay|
                                                            uzbek|venezuela|vietnam",
                                                            bertdf$country,
                                                            ignore.case = T),
                               "WL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2019&(bertdf$country=="CHINA"|
                                                     bertdf$country=="INDONESIA"|
                                                     bertdf$country=="INDIA"|
                                                     bertdf$country=="ALGERIA"|
                                                     bertdf$country=="KUWAIT"|
                                                     bertdf$country=="SAUDI ARABIA"|
                                                     bertdf$country=="RUSSIA"|
                                                     bertdf$country=="UKRAINE"|
                                                     bertdf$country=="ARGENTINA"|
                                                     bertdf$country=="CHILE"|
                                                     bertdf$country=="VENEZUELA"), "PWL")
bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2019&(bertdf$country=="THAILAND"|
                                                     bertdf$country=="VIETNAM"|
                                                     bertdf$country=="PAKISTAN"|
                                                     bertdf$country=="UZBEKISTAN"|
                                                     bertdf$country=="EGYPT"|
                                                     bertdf$country=="LEBANON"|
                                                     bertdf$country=="UNITE ARAB EMIRATES"|
                                                     bertdf$country=="GREECE"|
                                                     bertdf$country=="ROMANIA"|
                                                     bertdf$country=="SWITZERLAND"|
                                                     bertdf$country=="TURKEY"|
                                                     bertdf$country=="BARBADOS"|
                                                     bertdf$country=="BOLIVIA"|
                                                     bertdf$country=="BRAZIL"|
                                                     bertdf$country=="CANADA"|
                                                     bertdf$country=="COLOMBIA"|
                                                     bertdf$country=="COSTA RICA"|
                                                     bertdf$country=="DOMINICAN REPUBLIC"|
                                                     bertdf$country=="ECUADOR"|
                                                     bertdf$country=="GUATEMALA"|
                                                     bertdf$country=="JAMAICA"|
                                                     bertdf$country=="MEXICO"|
                                                     bertdf$country=="PARAGUAY"|
                                                     bertdf$country=="PERU"), "WL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2020&(bertdf$country=="CHINA"|
                                                     bertdf$country=="INDONESIA"|
                                                     bertdf$country=="INDIA"|
                                                     bertdf$country=="ALGERIA"|
                                                     bertdf$country=="SAUDI ARABIA"|
                                                     bertdf$country=="RUSSIA"|
                                                     bertdf$country=="UKRAINE"|
                                                     bertdf$country=="ARGENTINA"|
                                                     bertdf$country=="CHILE"|
                                                     bertdf$country=="VENEZUELA"), "PWL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2020&(bertdf$country=="THAILAND"|
                                                     bertdf$country=="VIETNAM"|
                                                     bertdf$country=="PAKISTAN"|
                                                     bertdf$country=="UZBEKISTAN"|
                                                     bertdf$country=="EGYPT"|
                                                     bertdf$country=="KUWAIT"|
                                                     bertdf$country=="LEBANON"|
                                                     bertdf$country=="UNITE ARAB EMIRATES"|
                                                     bertdf$country=="ROMANIA"|
                                                     bertdf$country=="TURKEY"|
                                                     bertdf$country=="BARBADOS"|
                                                     bertdf$country=="BOLIVIA"|
                                                     bertdf$country=="BRAZIL"|
                                                     bertdf$country=="CANADA"|
                                                     bertdf$country=="COLOMBIA"|
                                                     bertdf$country=="DOMINICAN REPUBLIC"|
                                                     bertdf$country=="ECUADOR"|
                                                     bertdf$country=="GUATEMALA"|
                                                     bertdf$country=="MEXICO"|
                                                     bertdf$country=="PARAGUAY"|
                                                     bertdf$country=="PERU"), "WL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2021&(bertdf$country=="CHINA"|
                                                     bertdf$country=="INDONESIA"|
                                                     bertdf$country=="INDIA"|
                                                     bertdf$country=="SAUDI ARABIA"|
                                                     bertdf$country=="RUSSIA"|
                                                     bertdf$country=="UKRAINE"|
                                                     bertdf$country=="ARGENTINA"|
                                                     bertdf$country=="CHILE"|
                                                     bertdf$country=="VENEZUELA"), "PWL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2021&(bertdf$country=="THAILAND"|
                                                     bertdf$country=="VIETNAM"|
                                                     bertdf$country=="PAKISTAN"|
                                                     bertdf$country=="UZBEKISTAN"|
                                                     bertdf$country=="EGYPT"|
                                                     bertdf$country=="KUWAIT"|
                                                     bertdf$country=="LEBANON"|
                                                     bertdf$country=="UNITE ARAB EMIRATES"|
                                                     bertdf$country=="ROMANIA"|
                                                     bertdf$country=="TURKEY"|
                                                     bertdf$country=="BARBADOS"|
                                                     bertdf$country=="BOLIVIA"|
                                                     bertdf$country=="BRAZIL"|
                                                     bertdf$country=="CANADA"|
                                                     bertdf$country=="COLOMBIA"|
                                                     bertdf$country=="DOMINICAN REPUBLIC"|
                                                     bertdf$country=="ECUADOR"|
                                                     bertdf$country=="GUATEMALA"|
                                                     bertdf$country=="MEXICO"|
                                                     bertdf$country=="PARAGUAY"|
                                                     bertdf$country=="PERU"|
                                                     bertdf$country=="ALGERIA"), "WL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2022&(bertdf$country=="CHINA"|
                                                     bertdf$country=="INDONESIA"|
                                                     bertdf$country=="INDIA"|
                                                     bertdf$country=="RUSSIA"|
                                                     bertdf$country=="ARGENTINA"|
                                                     bertdf$country=="CHILE"|
                                                     bertdf$country=="VENEZUELA"), "PWL")

bertdf$special301=replace(bertdf$special301,
                             bertdf$year==2022&(bertdf$country=="THAILAND"|
                                                     bertdf$country=="VIETNAM"|
                                                     bertdf$country=="PAKISTAN"|
                                                     bertdf$country=="UZBEKISTAN"|
                                                     bertdf$country=="EGYPT"|
                                                     bertdf$country=="ROMANIA"|
                                                     bertdf$country=="TURKEY"|
                                                     bertdf$country=="BARBADOS"|
                                                     bertdf$country=="BOLIVIA"|
                                                     bertdf$country=="BRAZIL"|
                                                     bertdf$country=="CANADA"|
                                                     bertdf$country=="COLOMBIA"|
                                                     bertdf$country=="DOMINICAN REPUBLIC"|
                                                     bertdf$country=="ECUADOR"|
                                                     bertdf$country=="GUATEMALA"|
                                                     bertdf$country=="MEXICO"|
                                                     bertdf$country=="PARAGUAY"|
                                                     bertdf$country=="PERU"|
                                                     bertdf$country=="ALGERIA"), "WL")

bertdf$country = str_to_title(bertdf$country)

bertdf$special301 = replace(bertdf$special301, bertdf$special301=="", NA)

bertdf$priority_watch = ifelse(bertdf$special301=="PWL", 1, 0)
bertdf$special301_all = ifelse(!is.na(bertdf$special301), 1, 0)

bertdf = bertdf %>%
  dplyr::group_by(country) %>%
  dplyr::mutate(
    lag_sp301 = dplyr::lag(special301),
    pwl_elev = ifelse(special301=="PWL"&(lag_sp301=="WL"|
                                           is.na(lag_sp301)|
                                           lag_sp301==""),
                      1, 0),
    pwl_deesc = ifelse(lag_sp301=="PWL"& (special301!="PWL"&special301!="PFC"), 1, 0)
  ) %>% dplyr::select(-lag_sp301)

bertdf$priority_watch = replace(bertdf$priority_watch, 
                                   is.na(bertdf$priority_watch), 0)
bertdf$pwl_elev = replace(bertdf$pwl_elev,
                             is.na(bertdf$pwl_elev), 0)
bertdf$pwl_deesc = replace(bertdf$pwl_deesc,
                             is.na(bertdf$pwl_deesc), 0)

```



## ISDS cases
```{r}
## ISDS cases
isds_us=read.csv("isds_cases_us_claim.csv")
colnames(isds_us)=c("year","isds_case_no", "claimant", "country", "status")

isds_us=isds_us %>%
  dplyr::group_by(country, year) %>%
  dplyr::summarise(
    isds_case_no = paste(isds_case_no, collapse = ", "),
    claimant = paste(claimant, collapse = ", "),
    isds_occurrences = n()
  )

isds_us$country = replace(isds_us$country, 
                          grepl("congo", isds_us$country, ignore.case = T),
                          "Congo")
isds_us$country = replace(isds_us$country, 
                          grepl("ecuador", isds_us$country, ignore.case = T),
                          "Ecuador")
isds_us$country = replace(isds_us$country, 
                          grepl("trinidad", isds_us$country, ignore.case = T),
                          "Trinidad and Tobago")

bertdf = bertdf %>%
  left_join(isds_us,
            by = c("country", "year"))

bertdf$isds_occurrences = replace(bertdf$isds_occurrences,
                                     is.na(bertdf$isds_occurrences), 0)

```


## GDP / Trade flows
```{r}
## GDP / tradeflow
gdppc = WDI(
  country = "all",
  indicator = "NY.GDP.PCAP.PP.KD",
  start = 1995,
  end = 2022,
  extra = T
)

gdpcons = WDI(
  country = "all",
  indicator = "NY.GDP.MKTP.PP.KD", #GDP PPP, constant 2021 USD
  start = 1995,
  end = 2022,
  extra = T
)

gdpgrowth = WDI(
  country = "all",
  indicator = "NY.GDP.MKTP.KD.ZG",
  start = 1995,
  end = 2022,
  extra = T
)

gdppc = gdppc %>% 
  dplyr::select(iso3c, year, NY.GDP.PCAP.PP.KD) %>%
  dplyr::mutate(gdppc = NY.GDP.PCAP.PP.KD) %>% dplyr::select(-NY.GDP.PCAP.PP.KD)
gdpcons = gdpcons %>% 
  dplyr::select(iso3c, year, NY.GDP.MKTP.PP.KD) %>%
  dplyr::mutate(gdpcons = NY.GDP.MKTP.PP.KD) %>% dplyr::select(-NY.GDP.MKTP.PP.KD)
gdpgrowth = gdpgrowth %>% 
  dplyr::select(iso3c, year, NY.GDP.MKTP.KD.ZG) %>%
  dplyr::mutate(gdpgrowth = NY.GDP.MKTP.KD.ZG) %>% dplyr::select(-NY.GDP.MKTP.KD.ZG)

bertdf = bertdf %>%
  left_join(gdppc,by = c("iso3c", "year")) %>%
  left_join(gdpcons, by = c("iso3c", "year")) %>%
  left_join(gdpgrowth, by = c("iso3c", "year"))

tradeflow_us = read.csv("dots_us.csv")
tradeflow_us = tradeflow_us %>% dplyr::select(
  Counterpart.Country.Name,
  Counterpart.Country.Code,
  Time.Period,
  Goods..Value.of.Imports..Cost..Insurance..Freight..CIF...US.Dollars..TMG_CIF_USD.,
  Goods..Value.of.Exports..Free.on.board..FOB...US.Dollars..TXG_FOB_USD.
)
colnames(tradeflow_us) = c("partner", "cc_imf", "year", "import", "export")
tradeflow_us = tradeflow_us %>% dplyr::mutate(
  iso3c = countrycode(cc_imf, "imf", "iso3c", custom_match = c("998" = "EUU"))
) %>% dplyr::select(-c(partner, cc_imf))

bertdf = bertdf %>%
  left_join(tradeflow_us, by = c("iso3c", "year"))

bertdf = bertdf %>%
  dplyr::mutate(
    log_import = sign(import)*log(abs(import)),
    log_export = sign(export)*log(abs(export)),
    log_gdppc = log(gdppc),
    log_gdpcons = log(gdpcons)
  )
```



## WhoGov
```{r}
whogov = read_csv("WhoGov_crosssectional_V2.0.csv")
whogov = whogov %>%
  dplyr::mutate(
    iso3c = country_isocode,
    regime_type = system_category
  ) %>%
  select(iso3c, year, leader, leader_party, regime_type)

bertdf = bertdf %>%
  left_join(whogov,
            by = c("iso3c", "year"))


bertdf = bertdf %>% 
  dplyr::group_by(country) %>%
  dplyr::mutate(
    leader_t1 = dplyr::lag(leader),
    party_t1 = dplyr::lag(leader_party),
    leader_change = ifelse(leader!=leader_t1, 1, 0),
    leader_pty_change = ifelse(leader_party!=party_t1, 1, 0)
  ) %>% dplyr::select(-c(leader_t1, party_t1)) %>%
  fill(c("leader_change", "leader_pty_change"), .direction = "up")

bertdf = bertdf %>%
  group_by(country) %>%
  dplyr::mutate(
    democ = ifelse(grepl("democra", regime_type, ignore.case = T) &
                     !is.na(regime_type), 1, NA)
  ) %>%
  fill(democ, .direction = "down")

bertdf = bertdf %>%
  group_by(country) %>%
  dplyr::mutate(
    dictatorship = ifelse(grepl("dictator", regime_type, ignore.case = T) &
                     !is.na(regime_type), 1, NA)
  ) %>%
  fill(dictatorship, .direction = "down")

bertdf$democ = replace(bertdf$democ, is.na(bertdf$democ), 0)
bertdf$dictatorship = replace(bertdf$dictatorship, is.na(bertdf$dictatorship), 0)
```



## WTO dev status
```{r}
wto_dev = c("Albania", "Antigua", "Argentina", "Armenia",
            "Bahrain", "Barbados", "Belize", "Bolivia",
            "Botswana", "Brazil", "Brunei", "Verde",
            "Cameroon", "Chile", "China", "Taipei",
            "Colombia", "Congo", "Costa Rica", "Ivoire",
            "Cuba", "Dominica", "Dominican Republic", "Ecuador",
            "Egypt", "El Salvador", "Eswatini", "Fiji", "Gabon",
            "Georgia", "Ghana", "Grenada", "Guatemala", "Guyana",
            "Honduras", "Hong Kong", "India", "Indonesia",
            "Israel", "Jamaica", "Jordan", "Kazakhstan",
            "Kenya", "Korea", "Kuwait", "Kyrgyz", "Macao",
            "Malaysia", "Maldives", "Mauritius", "Mexico",
            "Moldova", "Mongolia", "Montenegro", "Morocco",
            "Namibia", "Nicaragua", "Nigeria", "Macedonia",
            "Oman", "Pakistan", "Panama", "Papua New Guinea",
            "Paraguay", "Peru", "Philippines", "Qatar",
            "Kitts", "Lucia", "Grenadines",
            "Samoa", "Saudi Arabia", "Seychelles", "Singapore",
            "South Africa", "Sri Lanka", "Suriname", "Tajikistan",
            "Thailand", "Tonga", "Trinidad", "Tunisia", "Turkey",
            "Ukraine", "United Arab Emirates", "Uruguay", "Vanuatu",
            "Venezuela", "Viet", "Zimbabwe")

wto_ldc = c("Afghanistan", "Angola", "Bangladesh", "Benin",
            "Burkina Faso", "Burundi", "Cambodia", "Central African Republic",
            "Chad", "Congo", "Djibouti", "Gambia", "Guinea", "Bissau",
            "Haiti", "Laos", "Lesotho", "Liberia", "Madagascar",
            "Malawi", "Mali", "Mauritania", "Mozambique", "Myanmar",
            "Nepal", "Niger", "Rwanda", "Senegal", "Sierra Leone", "Solomon",
            "Tanzania", "Togo", "Uganda", "Yemen", "Zambia")

bertdf = bertdf %>%
  dplyr::mutate(
    wtodev = ifelse(grepl(paste0(wto_dev, collapse = "|"), country, ignore.case = T),
                    1, 0),
    wtoldc = ifelse(grepl(paste0(wto_ldc, collapse = "|"), country, ignore.case = T),
                    1, 0)
  )

bertdf$wtodev = replace(bertdf$wtodev, 
                           grepl("korea", bertdf$country, ignore.case = T) &
                             bertdf$year>2019, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("albania", bertdf$country, ignore.case = T) &
                             bertdf$year<2000, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("armenia", bertdf$country, ignore.case = T) &
                             bertdf$year<2003, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("verde", bertdf$country, ignore.case = T) &
                             bertdf$year<2008, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("china", bertdf$country, ignore.case = T) &
                             bertdf$year<2001, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("congo", bertdf$country, ignore.case = T) &
                             bertdf$year<1997, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("croatia", bertdf$country, ignore.case = T) &
                             bertdf$year<2000, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("georgia", bertdf$country, ignore.case = T) &
                             bertdf$year<2000, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("jordan", bertdf$country, ignore.case = T) &
                             bertdf$year<2000, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("kazakh", bertdf$country, ignore.case = T) &
                             bertdf$year<2015, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("kyrgyz", bertdf$country, ignore.case = T) &
                             bertdf$year<1998, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("laos", bertdf$country, ignore.case = T) &
                             bertdf$year<2013, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("latvia", bertdf$country, ignore.case = T) &
                             bertdf$year<1999, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("lithuania", bertdf$country, ignore.case = T) &
                             bertdf$year<2001, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("moldova", bertdf$country, ignore.case = T) &
                             bertdf$year<2001, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("mongol", bertdf$country, ignore.case = T) &
                             bertdf$year<1997, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("montenegro", bertdf$country, ignore.case = T) &
                             bertdf$year<2012, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("macedonia", bertdf$country, ignore.case = T) &
                             bertdf$year<2003, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("oman", bertdf$country, ignore.case = T) &
                             bertdf$year<2000, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("panama", bertdf$country, ignore.case = T) &
                             bertdf$year<1997, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("papua", bertdf$country, ignore.case = T) &
                             bertdf$year<1996, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("qatar", bertdf$country, ignore.case = T) &
                             bertdf$year<1996, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("russia", bertdf$country, ignore.case = T) &
                             bertdf$year<2012, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("samo", bertdf$country, ignore.case = T) &
                             bertdf$year<2012, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("saudi", bertdf$country, ignore.case = T) &
                             bertdf$year<2005, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("tajik", bertdf$country, ignore.case = T) &
                             bertdf$year<2013, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("ukraine", bertdf$country, ignore.case = T) &
                             bertdf$year<2008, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("emirates", bertdf$country, ignore.case = T) &
                             bertdf$year<1996, 0)
bertdf$wtodev = replace(bertdf$wtodev,
                           grepl("viet", bertdf$country, ignore.case = T) &
                             bertdf$year<1997, 0)
```



## UNGA / US aid
```{r}
unga = read.csv("unga_score.csv")
unga = unga %>% filter(ccode1==2, year>=1995) %>%
  dplyr::mutate(iso3c = countrycode(ccode2, "cown" , "iso3c", custom_match = c("995" = "EUU")),
                unga_dist = IdealPointDistance) %>%
  select(iso3c, year, unga_dist)

bertdf = bertdf %>%
  left_join(unga,
            by = c("iso3c", "year"))

## US aid
usaid = read.csv("us_foreign_aid_country.csv")
usaid = usaid[!grepl("region", usaid$Country.Name, ignore.case = T),]
names(usaid)[names(usaid) == "Fiscal.Year"] = "year" # oct1-sep30 (year in which it ends)
names(usaid)[names(usaid) == "Country.Code"] = "iso3c"
names(usaid)[names(usaid) == "Transaction.Type.Name"] = "trans_type"
usaid$year = as.numeric(usaid$year)
usaid = usaid[!is.na(usaid$year),]

usaid = usaid %>% 
  dplyr::select(iso3c, year, trans_type, constant_amount) %>%
  dplyr::mutate(aid_usd = constant_amount) %>%
  dplyr::select(-constant_amount)

usaid_disb = usaid[usaid$trans_type == "Disbursements",]
usaid_obl = usaid[usaid$trans_type == "Obligations",]
usaid_app = usaid[usaid$trans_type == "Appropriated and Planned",]

names(usaid_disb)[names(usaid_disb) == "aid_usd"] = "aid_disb_usd"
names(usaid_app)[names(usaid_app) == "aid_usd"] = "aid_app_usd"
names(usaid_obl)[names(usaid_obl) == "aid_usd"] = "aid_obl_usd"

usaid_disb = usaid_disb %>% dplyr::select(-trans_type)
usaid_app = usaid_app %>% dplyr::select(-trans_type)
usaid_obl = usaid_obl %>% dplyr::select(-trans_type)

bertdf = bertdf %>%
  left_join(usaid_disb, by = c("iso3c", "year"))
bertdf = bertdf %>%
  left_join(usaid_app, by = c("iso3c", "year"))
bertdf = bertdf %>%
  left_join(usaid_obl, by = c("iso3c", "year"))

bertdf = bertdf %>%
  dplyr::mutate(
    across(starts_with("aid_"), ~replace_na(., 0))
  )

## rearrange columns
bertdf = bertdf %>% select(iso3c, everything())
```

## DESTA
```{r}
desta = desta::treaties_dyads %>%
  dplyr::select(iso1, iso2, number) %>%
  left_join(desta::content_coding, by = "number") %>%
  dplyr::filter(iso1==840|iso2==840)

desta$iso1 = replace(desta$iso1, desta$iso1==840, 704)
desta$iso3c = countrycode(desta$iso1, origin = "iso3n", destination = "iso3c")

destatemp = desta %>%
  dplyr::select(iso3c, year, starts_with("ipr_"), number)

tplus = read_excel("TRIPSplus.xlsx")
tplus = tplus[,-c(180:293)]
tplus = tplus %>%
  select(-JS_ID, -BaseTreaty, -PTA, 
         -Members, -date_signature, 
         -year_signature, -date_entry_into_force, 
         -year_entry_into_force) %>%
  rename("number" = "Number")

bertdf = bertdf %>%
  left_join(destatemp, by = c("iso3c", "year"))

bertdf = bertdf %>%
  left_join(tplus, by="number")

bertdf = bertdf %>%
  dplyr::group_by(country) %>%
  tidyr::fill(starts_with("ipr_"), .direction = "down")

bertdf = bertdf %>%
  dplyr::mutate(across(starts_with("ipr_"), ~replace(., is.na(.), 0))) %>%
  dplyr::mutate(across(starts_with("tripsplus_"), ~replace(., is.na(.), 0)))

```


## IFC investment services prep
```{r}
ifcsvc = read.csv("IFC_invest_svcs.csv")
ifcsvc = ifcsvc %>%
  filter(WB.Country.Code != 99 & grepl("loan|equity", Product.Line, ignore.case = T) & grepl("active|complete|disbursement", Status, ignore.case = T)) %>%
  mutate(iso3c = countrycode(WB.Country.Code, origin = "wb_api2c", destination = "iso3c"),
         ifc_loan = Total.IFC.investment.as.approved.by.Board.Million...USD.*10^6,
         year = format(as.Date(IFC.Approval.Date, format = "%m/%d/%Y"), "%Y"),
         year = as.numeric(as.character(year))) %>%
  replace_na(list(ifc_loan = 0)) %>%
  dplyr::group_by(iso3c,year) %>%
  dplyr::summarise(ifc_loan = log1p(sum(ifc_loan)))

bertdf = bertdf %>%
  left_join(ifcsvc, by = c("iso3c", "year")) %>%
  replace_na(list(ifc_loan = 0))
```


## Build temp (lags and factors)
```{r}
temp = bertdf %>%
  # left_join(ifcbd_df, by = c("country", "year")) %>%
  # replace_na(list(ifc_board = 0)) %>%
  # replace_na(list(patents = 0, trademarks = 0)) %>%
  group_by(country) %>%
  mutate(ldeberta_score = lag(deberta_score),
         lifc_loan = lag(ifc_loan),
                wtoall = ifelse(wtodev+wtoldc>0, 1, 0),
                lwtoall = lag(wtoall),
                ldemo = lag(democ),
                ldict = lag(dictatorship),
                lunga_dist = lag(unga_dist,2),
                loecd = lag(oecd),
                lwtodev1 = lag(wtodev),
                lwtodev = lag(wtodev),
                lusbit = lag(usbit),
                ldevdict = ldict*lwtodev,
                ldevdemo = ldemo*lwtodev,
                ldevdemoall = ldemo*lwtoall,
                devstat = ifelse(lwtodev+wtodev>0, 1, 0),
                logaid = sign(aid_obl_usd)*log1p(abs(aid_obl_usd)),
                laid_usd = lag(logaid),
         logaidsb = sign(aid_disb_usd)*log1p(abs(aid_disb_usd)),
         laid_dsb = lag(logaidsb)
                ) %>%
  dplyr::mutate(ldevdict = factor(ldevdict, levels = c(0, 1), labels = c("No", "Yes")),
                lwtodev = factor(lwtodev, levels = c(0, 1), labels = c("No", "Yes")),
                ldevdemo = factor(ldevdemo, levels = c(0, 1), labels = c("No", "Yes")),
                democ = factor(democ, levels = c(0, 1), labels = c("Non-democracy", "Democracy")),
                ldemo = factor(ldemo, levels = c(0, 1), labels = c("Non-democracy", "Democracy")),
              )
```


# Aid allocation & TRIPS (DeBERTa score)
## regressions
```{r}
## model specs
summary(feols_trips_aid1 <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c"))
summary(feols_trips_aid1p <- feols(ipr_tripsplus_patents ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c"))
summary(feols_trips_aid1e <- feols(ipr_tripsplus_enforcement ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c"))

## select obs used in the analyses
tempA = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy")
tempA = tempA[unlist(feols_trips_aid1$obs_selection),]
tempA1 = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy")
tempA1 = tempA1[unlist(feols_trips_aid1p$obs_selection),]
tempB = temp%>%filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy")
tempB = tempB[unlist(feols_trips_aid1e$obs_selection),]

```


## autocracy placebo
```{r}
cat("\n--- Aid: Undisclosed Info (autocracy-placebo) ---\n")
print(summary(ap1<-feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))
cat("\n--- Aid: Patent (autocracy-placebo) ---\n")
print(summary(ap2<-feols(ipr_tripsplus_patents ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))
cat("\n--- Aid: Enforcement (autocracy-placebo) ---\n")
print(summary(ap3<-feols(ipr_tripsplus_enforcement ~ ldeberta_score*laid_usd + unga_dist +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export +
                usbit + isds_occurrences|year,
              data = temp%>%filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))

## named objects for the placebo table (columns 1-3: Aid x Non-democracy)
pl_aid_u <- ap1
pl_aid_p <- ap2
pl_aid_e <- ap3
```




## marginal plots

```{r}
plot_comparisons(
  feols_trips_aid1,
  variables = list("laid_usd"="sd"),
  condition = "ldeberta_score",
  conf_level = 0.95
) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data = tempA, aes(x = ldeberta_score), 
           inherit.aes = FALSE, color = "black", alpha = 0.4,
           length = unit(0.06, "npc")) +
  theme_classic() +
  xlab("DeBERTa Score") +
  ylab(bquote(Delta ~ ("Undisclosed info"))) +
  theme(
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent", color = NA),
    legend.position = "none"
  )

plot_comparisons(
  feols_trips_aid1p,
  variables = list("laid_usd"="sd"),
  condition = "ldeberta_score",
  conf_level = 0.9
) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data = tempA1, aes(x = ldeberta_score), 
           inherit.aes = FALSE, color = "black", alpha = 0.4,
           length = unit(0.06, "npc")) +
  theme_classic() +
  xlab("DeBERTa Score") +
  ylab(bquote(Delta ~ ("Patent"))) +
  theme(
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent", color = NA),
    legend.position = "none"
  )

plot_comparisons(
  feols_trips_aid1e,
  variables = list("laid_usd"="sd"),
  condition = "ldeberta_score",
  conf_level = 0.9
) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data = tempB, aes(x = ldeberta_score), 
           inherit.aes = FALSE, color = "black", alpha = 0.4,
           length = unit(0.06, "npc")) +
  theme_classic() +
  xlab("DeBERTa Score") +
  ylab(bquote(Delta ~ ("Enforcement"))) +
  theme(
    panel.background = element_rect(fill = "transparent"),
    plot.background = element_rect(fill = "transparent", color = NA),
    legend.position = "none"
  )

```



# IFC investment services & TRIPS
## regressions
```{r}
cat("\n--- IFC: Undisclosed Info ---\n")
print(summary(feols_trips_ifc1 <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*lifc_loan + 
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))
cat("\n--- IFC: Patent ---\n")
print(summary(feols_trips_ifc1p <- feols(ipr_tripsplus_patents ~ ldeberta_score*lifc_loan + 
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))
cat("\n--- IFC: Enforcement ---\n")
print(summary(feols_trips_ifc1e <- feols(ipr_tripsplus_enforcement ~ ldeberta_score*lifc_loan + 
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy"), cluster = "iso3c")))

tempC = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy")
tempC = tempC[unlist(feols_trips_ifc1$obs_selection),]
tempC1 = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy")
tempC1 = tempC1[unlist(feols_trips_ifc1p$obs_selection),]
tempD = temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS")%>%filter(democ=="Non-democracy")
tempD = tempD[unlist(feols_trips_ifc1e$obs_selection),]

```


## democracy placebo
```{r}
cat("\n--- IFC: Undisclosed Info (Democracy-placebo) ---\n")
print(summary(pl_ifc_u <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*lifc_loan +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c")))
cat("\n--- IFC: Patent (Democracy-placebo) ---\n")
print(summary(pl_ifc_p <- feols(ipr_tripsplus_patents ~ ldeberta_score*lifc_loan +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c")))
cat("\n--- IFC: Enforcement (Democracy-placebo) ---\n")
print(summary(pl_ifc_e <- feols(ipr_tripsplus_enforcement ~ ldeberta_score*lifc_loan +
                log_gdppc + log_gdpcons + gdpgrowth +
                log_import + log_export + lunga_dist +
                usbit + isds_occurrences|year,
              data = temp %>% filter(oecd1994==0 & iso3c!="EUU")%>%filter(democ=="Democracy"), cluster = "iso3c")))
```

## placebo table (LaTeX)
```{r}
etable(pl_aid_u, pl_aid_p, pl_aid_e, pl_ifc_u, pl_ifc_p, pl_ifc_e,
       tex = TRUE,
       depvar = TRUE,
       digits = "r3",
       digits.stats = "r3",
       fitstat = ~ n + r2 + wr2,
       signifCode = c("**" = 0.01, "*" = 0.05, "+" = 0.10),
       file = "placebo_table.tex",
       replace = TRUE)
cat("Wrote placebo_table.tex:", file.exists("placebo_table.tex"), "\n")
```



## marginal plots
```{r}
plot_comparisons(feols_trips_ifc1,
            variables = list("lifc_loan" = "sd"), 
            condition = c("ldeberta_score"),
            conf_level = 0.9) +
  theme_classic() + xlab("DeBERTa score") + ylab(bquote(Delta ~ ("Undisclosed info"))) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data=tempC, aes(x=ldeberta_score), color = "black", alpha = .4, length = unit(0.06, "npc")) +
  theme(
         panel.background = element_rect(fill='transparent'),
         plot.background = element_rect(fill='transparent', color=NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         legend.position = "none"
       )

plot_comparisons(feols_trips_ifc1p,
            variables = list("lifc_loan" = "sd"), 
            condition = c("ldeberta_score"),
            conf_level = 0.9) +
  theme_classic() + xlab("DeBERTa score") + ylab(bquote(Delta ~ ("Patent"))) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data=tempC1, aes(x=ldeberta_score), color = "black", alpha = .4, length = unit(0.06, "npc")) +
  theme(
         panel.background = element_rect(fill='transparent'),
         plot.background = element_rect(fill='transparent', color=NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         legend.position = "none"
       )

plot_comparisons(feols_trips_ifc1e,
            variables = list("lifc_loan" = "sd"), 
            condition = c("ldeberta_score"),
            conf_level = 0.9) +
  theme_classic() + xlab("DeBERTa score") + ylab(bquote(Delta ~ ("Enforcement"))) +
  geom_hline(yintercept = 0, color = "grey80", linetype = "dashed") +
  geom_rug(data=tempD, aes(x=ldeberta_score), color = "black", alpha = .4, length = unit(0.06, "npc")) +
  theme(
         panel.background = element_rect(fill='transparent'),
         plot.background = element_rect(fill='transparent', color=NA),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         legend.position = "none"
       )

```



# Results table
```{r}
etable(feols_trips_aid1, feols_trips_aid1e,
       feols_trips_ifc1, feols_trips_ifc1e,
       tex = T, depvar = T, digits = "r3", digits.stats = "r3")
```



# Heckman Selection Model (Robustness Check)
```{r heckman-setup}
load_pkg <- function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg, repos = "https://cloud.r-project.org")
  }
  library(pkg, character.only = TRUE)
}
invisible(lapply(c("sampleSelection", "texreg"), load_pkg))
```

```{r heckman-data}
# Panel Heckman: use bertdf (country-year) directly
# Selection eq: uspta (1 = has US PTA in force) — already in bertdf
# Outcome eq: TRIPS-plus depth conditional on uspta == 1
# Exclusion restriction: log geographic distance from US (CEPII GeoDist)
# Rationale: distance predicts PTA formation (gravity) but should not
# directly determine the depth of TRIPS-plus provisions conditional on signing

# Load CEPII bilateral distance data
dist_cepii <- read_xls("dist_cepii.xls")
us_dist <- dist_cepii %>%
  filter(iso_o == "USA") %>%
  select(iso_d, distcap) %>%
  rename(iso3c = iso_d, dist_us = distcap) %>%
  mutate(log_dist_us = log(dist_us))

# Merge into temp
temp <- temp %>%
  left_join(us_dist, by = "iso3c")

cat("Panel observations:", nrow(temp), "\n")
cat("Missing log_dist_us:", sum(is.na(temp$log_dist_us)), "\n")
cat("uspta = 1:", sum(temp$uspta == 1, na.rm = TRUE), "\n")
```


```{r heckman-divided-gov-data}
# Strict Kersting-style coding: divided_gov = 1 only when BOTH chambers
# of Congress are controlled by the party opposite to the sitting
# president (i.e., genuine split-party control of the legislature).
# Any configuration where the president's party holds at least one
# chamber is coded as unified (0).
#
# 10 divided years (1995-2000, 2007-2008, 2015-2016), 18 unified years.
# More restrictive than a lenient "either-chamber-opposite" coding;
# identifies the political episodes in which congressional constraints
# on executive-discretion aid policy bind most tightly.

divided_gov_df <- tibble::tibble(
  year = 1995:2022,
  divided_gov = c(
    1,1,1,1,1,1,   # 1995-2000 Clinton (D), R House + R Senate
    0,0,           # 2001-2002 Bush (R), only Senate opposite (not both)
    0,0,0,0,       # 2003-2006 Bush (R), unified R Congress
    1,1,           # 2007-2008 Bush (R), D House + D Senate
    0,0,           # 2009-2010 Obama (D), unified D Congress
    0,0,0,0,       # 2011-2014 Obama (D), only House opposite (not both)
    1,1,           # 2015-2016 Obama (D), R House + R Senate
    0,0,           # 2017-2018 Trump (R), unified R Congress
    0,0,           # 2019-2020 Trump (R), only House opposite (not both)
    0,0            # 2021-2022 Biden (D), unified D Congress
  )
)

heck_demo <- temp %>% filter(oecd1994==0 & iso3c!="EUU") %>% filter(democ=="Democracy")
heck_nondem <- temp %>% filter(oecd1994==0 & iso3c!="EUU" & iso3c!="RUS") %>% filter(democ=="Non-democracy")

heck_demo_dg   <- heck_demo   %>% left_join(divided_gov_df, by = "year")
heck_nondem_dg <- heck_nondem %>% left_join(divided_gov_df, by = "year")

cat("Democracy subsample: strict divided_gov distribution\n")
print(table(heck_demo_dg$divided_gov, useNA = "ifany"))
cat("Non-democracy subsample: strict divided_gov distribution\n")
print(table(heck_nondem_dg$divided_gov, useNA = "ifany"))
```

```{r heckman-aid-dg-models}
# Aid x Democracy Heckman with:
#  - strict divided_gov replacing post2002
#  - usbit, log_export, gdpgrowth added to baseline controls
# Exclusion restriction in selection equation: log_dist_us (gravity).

heck_aid_undisc_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_undisclosed_information ~ ldeberta_score * laid_usd +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_demo_dg, method = "2step")

heck_aid_patent_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_patents ~ ldeberta_score * laid_usd +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_demo_dg, method = "2step")

heck_aid_enf_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_enforcement ~ ldeberta_score * laid_usd +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_demo_dg, method = "2step")
```

```{r heckman-ifc-dg-models}
# IFC x Non-democracy Heckman: same expanded controls.

heck_ifc_undisc_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_undisclosed_information ~ ldeberta_score * lifc_loan +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_nondem_dg, method = "2step")

heck_ifc_patent_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_patents ~ ldeberta_score * lifc_loan +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_nondem_dg, method = "2step")

heck_ifc_enf_dg <- heckit(
  uspta ~ log_dist_us + log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  ipr_tripsplus_enforcement ~ ldeberta_score * lifc_loan +
          log_gdpcons + log_import + log_export + unga_dist +
          usbit + gdpgrowth + divided_gov,
  data = heck_nondem_dg, method = "2step")
```

```{r heckman-dg-results}
dg_models <- list(
  "Aid x Democracy: Undiscl"  = heck_aid_undisc_dg,
  "Aid x Democracy: Patents"  = heck_aid_patent_dg,
  "Aid x Democracy: Enforce"  = heck_aid_enf_dg,
  "IFC x Non-dem:  Undiscl"   = heck_ifc_undisc_dg,
  "IFC x Non-dem:  Patents"   = heck_ifc_patent_dg,
  "IFC x Non-dem:  Enforce"   = heck_ifc_enf_dg
)

sig_stars <- function(p) ifelse(is.na(p), "",
  ifelse(p < 0.01, "**", ifelse(p < 0.05, "*",
  ifelse(p < 0.10, "+", ""))))

cat("\n=== Strict divided-gov + usbit + log_export + gdpgrowth ===\n")
for (m_name in names(dg_models)) {
  s <- summary(dg_models[[m_name]])
  coefs <- s$estimate
  rows  <- rownames(coefs)
  main_var  <- if (grepl("Aid", m_name)) "laid_usd" else "lifc_loan"
  inter_var <- paste0("ldeberta_score:", main_var)

  lvl <- coefs[rows == main_var,  , drop = FALSE]
  itr <- coefs[rows == inter_var, , drop = FALSE]
  imr <- coefs[rows == "invMillsRatio", , drop = FALSE]

  cat(sprintf("\n-- %s --\n", m_name))
  cat(sprintf("  Level  (%-9s)       :  %+8.4f  SE=%.4f  p=%.4f %s\n",
    main_var,  lvl[1,1], lvl[1,2], lvl[1,4], sig_stars(lvl[1,4])))
  cat(sprintf("  Inter  (%-24s):  %+8.4f  SE=%.4f  p=%.4f %s\n",
    inter_var, itr[1,1], itr[1,2], itr[1,4], sig_stars(itr[1,4])))
  if (nrow(imr) > 0) {
    cat(sprintf("  IMR    (invMillsRatio)       :  %+8.4f  SE=%.4f  p=%.4f %s\n",
      imr[1,1], imr[1,2], imr[1,4], sig_stars(imr[1,4])))
  }
}

screenreg(dg_models,
          custom.model.names = c("Aid:Und (D)", "Aid:Pat (D)", "Aid:Enf (D)",
                                 "IFC:Und (ND)","IFC:Pat (ND)","IFC:Enf (ND)"),
          digits = 3)

# Export LaTeX table for manuscript (overwrites heckman_results.tex)
texreg(dg_models,
       custom.model.names = c("Undiscl (D)", "Patents (D)", "Enforce (D)",
                              "Undiscl (ND)","Patents (ND)","Enforce (ND)"),
       caption = "Heckman selection model (strict divided-government specification)",
       label   = "tab:heckman",
       file    = "heckman_results.tex",
       digits  = 3,
       stars   = c(0.01, 0.05, 0.10))
cat("Saved heckman_results.tex (divided-gov spec)\n")
```




# Summary stats (analysis sample: non-OECD, excl EU)
```{r}
# Overall analysis sample
all_vars <- temp %>%
  filter(oecd1994==0 & iso3c!="EUU") %>%
  ungroup() %>%
  select(ipr_tripsplus_undisclosed_information, ipr_tripsplus_patents, ipr_tripsplus_enforcement,
         ldeberta_score, laid_usd, lifc_loan, unga_dist,
         log_gdppc, log_gdpcons, gdpgrowth,
         log_import, log_export, usbit, isds_occurrences, democ) %>%
  drop_na()

cat("=== OVERALL SAMPLE ===\n")
cat(sprintf("N = %d, Democracy share = %.3f\n\n", nrow(all_vars), mean(all_vars$democ=="Democracy")))
for (v in setdiff(names(all_vars), "democ")) {
  x <- all_vars[[v]]
  cat(sprintf("%-45s  Mean=%8.3f  SD=%8.3f  Min=%8.3f  Max=%8.3f\n",
    v, mean(x), sd(x), min(x), max(x)))
}

# Democracy subsample (aid models)
cat("\n=== DEMOCRACY SUBSAMPLE (aid models) ===\n")
demo_vars <- all_vars %>% filter(democ=="Democracy") %>% select(-democ)
cat(sprintf("N = %d\n\n", nrow(demo_vars)))
for (v in names(demo_vars)) {
  x <- demo_vars[[v]]
  cat(sprintf("%-45s  Mean=%8.3f  SD=%8.3f  Min=%8.3f  Max=%8.3f\n",
    v, mean(x), sd(x), min(x), max(x)))
}

# Non-democracy subsample (IFC models)
cat("\n=== NON-DEMOCRACY SUBSAMPLE (IFC models) ===\n")
nondem_vars <- all_vars %>% filter(democ=="Non-democracy") %>% select(-democ)
cat(sprintf("N = %d\n\n", nrow(nondem_vars)))
for (v in names(nondem_vars)) {
  x <- nondem_vars[[v]]
  cat(sprintf("%-45s  Mean=%8.3f  SD=%8.3f  Min=%8.3f  Max=%8.3f\n",
    v, mean(x), sd(x), min(x), max(x)))
}
```


# Identification robustness: TWFE and Mundlak

## Main channel — Aid x Democracy (TWFE)
```{r robust-aid-yfe}
ce_aid <- "log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist"
demo_main <- temp %>% filter(oecd1994==0 & iso3c!="EUU") %>% filter(democ=="Democracy")
aid_yfe_u <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*laid_usd + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist |iso3c+year, data=demo_main, cluster="iso3c")
aid_yfe_p <- feols(ipr_tripsplus_patents                 ~ ldeberta_score*laid_usd + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist |iso3c+year, data=demo_main, cluster="iso3c")
aid_yfe_e <- feols(ipr_tripsplus_enforcement             ~ ldeberta_score*laid_usd + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist |iso3c+year, data=demo_main, cluster="iso3c")
etable(aid_yfe_u, aid_yfe_p, aid_yfe_e, tex=TRUE, file="table_aid_dem_yfe.tex", digits=3)
```

## Main channel — Aid x Democracy (Mundlak)
```{r robust-aid-mundlak}
demo_mund <- demo_main %>% group_by(iso3c) %>%
  mutate(mean_aid = mean(laid_usd, na.rm=TRUE),
         dev_aid  = laid_usd - mean_aid) %>% ungroup()
aid_mk_u <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*dev_aid + ldeberta_score*mean_aid + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist | year, data=demo_mund, cluster="iso3c")
aid_mk_p <- feols(ipr_tripsplus_patents                 ~ ldeberta_score*dev_aid + ldeberta_score*mean_aid + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist | year, data=demo_mund, cluster="iso3c")
aid_mk_e <- feols(ipr_tripsplus_enforcement             ~ ldeberta_score*dev_aid + ldeberta_score*mean_aid + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + unga_dist | year, data=demo_mund, cluster="iso3c")
etable(aid_mk_u, aid_mk_p, aid_mk_e, tex=TRUE, file="table_aid_dem_mundlak.tex", digits=3)
```

## Main channel — IFC x Non-democracy (TWFE)
```{r robust-ifc-yfe}
nondem_main <- temp %>% filter(oecd1994==0 & iso3c!="EUU") %>% filter(democ=="Non-democracy")
ifc_yfe_u <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*lifc_loan + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist |iso3c+year, data=nondem_main, cluster="iso3c")
ifc_yfe_p <- feols(ipr_tripsplus_patents                 ~ ldeberta_score*lifc_loan + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist |iso3c+year, data=nondem_main, cluster="iso3c")
ifc_yfe_e <- feols(ipr_tripsplus_enforcement             ~ ldeberta_score*lifc_loan + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist |iso3c+year, data=nondem_main, cluster="iso3c")
etable(ifc_yfe_u, ifc_yfe_p, ifc_yfe_e, tex=TRUE, file="table_ifc_nondem_yfe.tex", digits=3)
```

## Main channel — IFC x Non-democracy (Mundlak)
```{r robust-ifc-mundlak}
nondem_mund <- nondem_main %>% group_by(iso3c) %>%
  mutate(mean_ifc = mean(lifc_loan, na.rm=TRUE),
         dev_ifc  = lifc_loan - mean_ifc) %>% ungroup()
ifc_mk_u <- feols(ipr_tripsplus_undisclosed_information ~ ldeberta_score*dev_ifc + ldeberta_score*mean_ifc + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist | year, data=nondem_mund, cluster="iso3c")
ifc_mk_p <- feols(ipr_tripsplus_patents                 ~ ldeberta_score*dev_ifc + ldeberta_score*mean_ifc + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist | year, data=nondem_mund, cluster="iso3c")
ifc_mk_e <- feols(ipr_tripsplus_enforcement             ~ ldeberta_score*dev_ifc + ldeberta_score*mean_ifc + log_gdppc + log_gdpcons + gdpgrowth + log_import + log_export + usbit + isds_occurrences + lunga_dist | year, data=nondem_mund, cluster="iso3c")
etable(ifc_mk_u, ifc_mk_p, ifc_mk_e, tex=TRUE, file="table_ifc_nondem_mundlak.tex", digits=3)
```

## Save analysis dataset and convenience workspace
```{r save-extract-workspace}
write.csv(temp, "analysis_data.csv", row.names = FALSE)
save.image("nteDeBERTa_RR.RData")
cat("Wrote analysis_data.csv:", file.exists("analysis_data.csv"), "\n")
cat("Wrote nteDeBERTa_RR.RData:", file.exists("nteDeBERTa_RR.RData"), "\n")
```










